Network Visualizations in \MakeLowercase{\texttt{ggplot2}}

### 2015-10-12 inst/paper.Rnw
update on ggplot2 statistics ... they are pretty amazing!

% ggplot2 as an implementation framework
We found the current tools to be lacking in this ability, so we chose to fill this gap by adding network plotting capabilities to the popular and widely used \texttt{R} package \texttt{ggplot2}. Just to give an idea of the popularity and the wide-spread use of \texttt{ggplot2}, from January 1, 2015 to March 21, 2015, \texttt{ggplot2} was downloaded over 270,000 times, or approximately 3,454 downloads per day. It has also been downloaded in 189 countries at least once, and in 31 of those countries, including China, Israel, and Colombia, it has been downloaded over 1,000 times\footnote{\texttt{ggplot2} usage statistics taken from \url{http://cran-logs.rstudio.com/}.}. This is the user base we are aiming at by making network visualizations a part of \texttt{ggplot2}.

>>>>

% ggplot2 as an implementation framework
We found the current tools to be lacking in this ability, so we chose to fill this gap by adding network plotting capabilities to the popular and widely used \texttt{R} package \texttt{ggplot2}. Just to give an idea of the popularity and the wide-spread use of \texttt{ggplot2}, from January 1, 2015 to October 4, 2015, \texttt{ggplot2} was downloaded over 1.2 Million times, or approximately 4,342 downloads per day. It has also been downloaded in 215 countries at least once, and in 61 of those countries, including China, Israel, and Colombia, it has been downloaded over 1,000 times\footnote{\texttt{ggplot2} usage statistics taken from \url{http://cran-logs.rstudio.com/}.}. This is the user base we are aiming at by making network visualizations a part of \texttt{ggplot2}.
